Luminance constancy under fixed geometry

### 2018-01-27 Draft2/draft2.tex
edits

% WHAT STORY DO WE WANT TO TELL ABOUT THE RESULTS
%  1) Case 0 -- work out effect of sources of internal noise - isomerization and AMA -- without any external "noise", where external "noise" is the effect of variability in object extrinsic scene factors (illumination, surrounding objects). 
%                      Also establish the rendering noise is einsy relative to whatever else we're doing.
%  2) Move to Case 1 -- what happens when we introduce color variability into the target.  This may not be of interest to the psychophysics, but none-the-less seems interesting to know as one ponders lightness constancy.
%  3) On to Case 2 -- here the question is, do we keep varying target color, or do we fix target color and vary illumination?  In any case, this isn't too hard a case if the other objects remain fixed, because then contrast coding basically normalizes out a lot of the variation, and it's only the spectral variation that might screw things up.  But, that's why we run case 3.
%  4) Do we run a case where the relative spectrum of the illuminant stays fixed and we only vary intensity?
%  4) On to Case 3 --
\section{Results} \label{Results}
\begin{itemize}  
\item Show the minimal model (to describe the sources and magnitude of error). This can go in supplement.
\begin{itemize}  
\item rendering error
\item isomerization error
\item ama error
\end{itemize}
\item Case 1. Only the target object color changes. AMA on isomerization
\item Case 2. Background color changes too, AMA on isomerization. (This is not giving good results. The filters are giving weights to the background which they should not. Maybe more samples would help.)
\item Case 3. Background fixed, illuminant changes, AMA on isomerization fails, but the contrast version works
\item Case 4. Change all three and show that both ismerization fails, constrast does better, but not perfectly better

\end{itemize}

%% Figure Results
\begin{figure}
\centering
    \begin{subfigure}[b]{0.33 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingNoise.pdf}
        \caption{Rendering noise}
        \label{fig:renderingNoise}
    \end{subfigure}
        \begin{subfigure}[b]{0.33 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingAndIsomerization.pdf}
        \caption{Rendering and isomerization noise}
        \label{fig:renderingAndIsomerization}
    \end{subfigure}
        \begin{subfigure}[b]{0.33 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingIsomerizationTargetColor.pdf}
        \caption{Target color variation}
        \label{fig:renderingIsomerizationTargetColor}
    \end{subfigure}    
    \caption{Different sources of noise}
\label{fig:sourcesOfNoise}
\end{figure}

@@

%% Figure 9
\begin{figure}
\centering
    \begin{subfigure}[b]{0.4 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case9AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.27 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
        \caption{AMA RF Response}
        \label{fig:case9FiltersResponse}
    \end{subfigure}
        \begin{subfigure}[b]{0.27 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
        \caption{Luminance Estimates}
        \label{fig:case9Results}
    \end{subfigure}    
    \caption{{\bf Receptive fields and luminance estimates. Case 1:} (a) First two receptive fields produced by the AMA. Along the row we show the filters corresponding to the L cones, M cones and S cones (left to right). (b) The response of the stimuli to the first two AMA filters. The responses are grouped with the label of the stimuli. As is clear, the response distributions at each luminance level separate out well in this case, resulting in good estimates of the target object luminance. (c) The estimates of the target object standard luminance. The naive method produces the mean value of the target luminance used in the analysis. The shaded region corresponds to 1 sigma standard deviation.}
\label{fig:case9AllResults}
\end{figure}

>>>>

% WHAT STORY DO WE WANT TO TELL ABOUT THE RESULTS
%  1) Case 0 -- work out effect of sources of internal noise - isomerization and AMA -- without any external "noise", where external "noise" is the effect of variability in object extrinsic scene factors (illumination, surrounding objects). 
%                      Also establish the rendering noise is einsy relative to whatever else we're doing.
%  2) Move to Case 1 -- what happens when we introduce color variability into the target.  This may not be of interest to the psychophysics, but none-the-less seems interesting to know as one ponders lightness constancy.
%  3) On to Case 2 -- here the question is, do we keep varying target color, or do we fix target color and vary illumination?  In any case, this isn't too hard a case if the other objects remain fixed, because then contrast coding basically normalizes out a lot of the variation, and it's only the spectral variation that might screw things up.  But, that's why we run case 3.
%  4) Do we run a case where the relative spectrum of the illuminant stays fixed and we only vary intensity?
%  4) On to Case 3 --
\section{Results} \label{Results}
\begin{itemize}
\item Show the minimal model (to describe the sources and magnitude of error). This can go in supplement.
\begin{itemize}  
\item rendering error
\item isomerization error
\item ama error
\end{itemize}
\item Case 1. Only the target object color changes. AMA on isomerization
\item Case 2. Background color changes too, AMA on isomerization. (This is not giving good results. The filters are giving weights to the background which they should not. Maybe more samples would help.)
\item Case 3. Background fixed, illuminant changes, AMA on isomerization fails, but the contrast version works
\item Case 4. Change all three and show that both ismerization fails, constrast does better, but not perfectly better
\end{itemize}

\subsection{In the absence of illuminant and background variation, object lightness can be estimated directly from the photoreceptor response}

We used AMA to learn a set of linear receptive fields that are optimal for target object lightness estimation for images of case 1. 
Fig. \ref{fig:renderingIsomerizationTargetColor} shows the projection of the photoreceptor response along the first two receptive fields. 
Clearly, there exists a subspace along which the photoresponse response separates according to the luminance level assigned to the target object. 
The target object luminance of the images in the test set can thus be obtained by projecting the corresponding photoreceptor response along these AMA receptive fields. 
Fig.\ref{fig:case9Results} shows the estimated luminance for the test images in case 1 v/s the actual lightness assigned to the target object for AMA. 
We also show the estimates of two null models: a naive method that assigns the average luminance across the training set to all images, and a linear model based on the photoreceptors corresponding to the center pixel on the target object. 
As expected, in the absence of any external source of variation, the photoreceptor response is proportional to the luminance of the target object, and hence can be easily estimated by both AMA and linear regression.

Each cloud in Fig.\ref{fig:renderingIsomerizationTargetColor} corresponds to the photoreceptor response to the images with target luminance level at a fixed value. 
The variation within the cloud results due to the difference in shape of the target object reflectance spectra at the same luminance. 
This variation dominates any variation coming from the noise in photoreceptor response or the noisy rendering of the images by the software. 
Fig.\ref{fig:renderingAndIsomerization} shows the projection of photoreceptor response corresponding to 1000 images where, in addition to the illumination and background spectra, we also fixed the relative shape of the target object surface reflectance. 
Thus, for these images the target object had the same hue and chroma at all luminance levels.
Any variation resulting from the poisson nature of the photoreceptor response or due the image rendering software is negligible, and can be ignored.
(DO WE WANT TO GET AN ESTIMATE OF THE CLOUD SIZE FROM THE ALLOWED VARIATION IN THE SPECTRAL SHAPE?)

%% Figure Results
\begin{figure}
\centering
        \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingIsomerizationTargetColor.pdf}
        \caption{Target color variation}
        \label{fig:renderingIsomerizationTargetColor}
    \end{subfigure}    
%    \begin{subfigure}[b]{0.33 \textwidth}   
 %       \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingNoise.pdf}
%        \caption{Rendering noise}
%        \label{fig:renderingNoise}
%    \end{subfigure}
            \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
        \caption{Luminance Estimates}
        \label{fig:case9Results}
    \end{subfigure}    
        \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingAndIsomerization.pdf}
        \caption{Rendering and isomerization noise}
        \label{fig:renderingAndIsomerization}
    \end{subfigure}
    \caption{Different sources of noise}
\label{fig:sourcesOfNoise}
\end{figure}

@@

%% Figure 9
\begin{figure}
\centering
    \begin{subfigure}[b]{0.4 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case9AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.27 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
        \caption{AMA RF Response}
        \label{fig:case9FiltersResponse}
    \end{subfigure}
    \caption{{\bf Receptive fields and luminance estimates. Case 1:} (a) First two receptive fields produced by the AMA. Along the row we show the filters corresponding to the L cones, M cones and S cones (left to right). (b) The response of the stimuli to the first two AMA filters. The responses are grouped with the label of the stimuli. As is clear, the response distributions at each luminance level separate out well in this case, resulting in good estimates of the target object luminance. (c) The estimates of the target object standard luminance. The naive method produces the mean value of the target luminance used in the analysis. The shaded region corresponds to 1 sigma standard deviation.}
\label{fig:case9AllResults}
\end{figure}
